Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

\begin{deluxetable}{cc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & ??? & ??? \\
$n$  &  ???   & ???  \\
$C$ & ??? & ???  \\
$\alpha$  & not applicable    & ???  \\
$\beta$ & not applicable  & ??? \\
$\delta$ & not applicable & ??? \\
\enddata
\end{deluxetable}

>>>>

\begin{deluxetable}{cc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
$\beta$ & not applicable  & $1 - 10$ \\
$\delta$ & not applicable & $0.001\rightarrow 3$ \\
\enddata
\end{deluxetable}
